---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Aula de Introdução ao Machine Learning

**Professor:** Athos Damiani 

**Realização:** [ASN.rocks](https://asn.rocks/)

# Pré-requisitos

## Configuração: Instalar pacotes

```{r, eval=FALSE, echo = TRUE}
install.packages('tidyverse')
install.packages('tidymodels')
install.packages('rmarkdown')
install.packages('knitr')
install.packages('ISLR')
install.packages('glmnet')
install.packages('xgboost')
install.packages('randomForest')
install.packages('ranger')
install.packages('rpart')
install.packages('rpart.plot')
install.packages('pROC')
install.packages('vip')
install.packages('modeldata')
install.packages('usemodels')
install.packages('tidypredict')
install.packages('jpeg')
install.packages('MASS')
install.packages('DataExplorer')
install.packages('skimr')
install.packages('naniar')
install.packages('patchwork')
```


## Slides

```{r, echo = FALSE}
main_repo <- "asn-intro-ml"
knitr::kable(
  tibble::tibble(
    slide = list.files("slides/", "\\.html"),
    link = paste0("https://curso-r.github.io/", main_repo, "/slides/", slide)
  ) %>% 
    dplyr::filter(!stringr::str_detect(slide, "_files/")) %>% 
    dplyr::slice(1:3)
)
```

## Referências externas

#### Machine Learning

- [Introduction to Statistical Learning (Hastie, et al)](https://web.stanford.edu/~hastie/ISLRv2_website.pdf)
- [Elements of Statistical Learning (Hastie, et al)](https://web.stanford.edu/~hastie/Papers/ESLII.pdf)
- [Computer Age Statistical Inference (Hastie, Efron)](https://web.stanford.edu/~hastie/CASI_files/PDF/casi.pdf)
- [Tidymodels (Kuhn, et al)](https://www.tidymodels.org/)
- [Feature Engineering and Selection: A Practical Approach for Predictive Models (Kuhn, Kjell)](http://www.feat.engineering/)
- [Kaggle](https://www.kaggle.com/)

#### Programação em R

- [Livro da Curso-R (Curso-R)](https://livro.curso-r.com/)
- [Tidyverse (Wickham H)](https://www.tidyverse.org/)
- [R for Data Science (Wickham H)](https://r4ds.had.co.nz/)
- [Advanced R (Wickham H)](https://adv-r.hadley.nz/)

#### Miscelânea

- [Tidytext (Silges, et al)](https://www.tidytextmining.com/)
- [Tabnet model (Falbel)](https://mlverse.github.io/tabnet/)
- [Forecasting: Principles and Practive (Hyndman, Athanasopoulos)](https://otexts.com/fpp3/)

